**Fabryka**

### 2025-05-05 fabryka_pci/article.Rmd
Typos

To distinguish different statistical populations, a spatial method
proposed by McPherron (2018) is used. Thanks to this methods it is
possible to calculate the Benn indices and to test the orientation rate
'L' (formula (**3.**) modified R [@mcpherron2018] script) for each
remains, and its n nearest neighbours in 3 dimensions (McPherron
[-@mcpherron2018] R script, modified , formula (**4.**)). The analysis
of the fabric as proposed by McPherron [-@mcpherron2018] has the
advantage of spatialising the measurements and thus avoiding the
arbitrary sampling classically carried out by square and décapage. It
is possible to localize the statistical signal of fabrics by varying the
number of measurements sampled to calculate the Benn indices. The choice
of about 40 to 60 measurements (each remain and its 40 to 60 nearest
neighbours) to calculate the Benn indices allows local particularities
to be observed, and above all, it allows the Rayleigh test to be carried
out in its field of application (stability of the test between around 40
to 50 measurements after [-@bertran2002]).

>>>>

To distinguish different statistical populations, a spatial method
proposed by McPherron (2018) is used. Thanks to this method it is
possible to calculate the Benn indices and to test the orientation rate
'L' (formula (**3.**) modified R [@mcpherron2018] script) for each
remains, and its n nearest neighbours in 3 dimensions (McPherron
[-@mcpherron2018] R script, modified , formula (**4.**)). The analysis
of the fabric as proposed by McPherron [-@mcpherron2018] has the
advantage of spatialising the measurements and thus avoiding the
arbitrary sampling classically carried out by square and décapage. It
is possible to localize the statistical signal of fabrics by varying the
number of measurements sampled to calculate the Benn indices. The choice
of about 40 to 60 measurements (each remain and its 40 to 60 nearest
neighbours) to calculate the Benn indices allows local particularities
to be observed, and above all, it allows the Rayleigh test to be carried
out in its field of application (stability of the test between around 40
to 50 measurements after @bertran2002).
